### 2012-05-25 GUIErrorDetector/paper/implementation.tex
fix trivial issues in format

\item \textbf{Safe UI methods:}  \CodeIn{Display.asyncExec}
and \CodeIn{Display.syncExec}.
These methods
execute code (a)synchro\-nously on the UI thread.

@@

\tinystep
\tinystep
\subsubsection{Eclipse plugin}

@@

\item \textbf{UI-accessing nodes} and \textbf{Safe UI methods} are the same as SWT\@.

@@

\item \textbf{Safe UI methods:}  
\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{Swing\-Util\-ities.invokeAndWait}, which execute code on the UI thread.

@@

\item \textbf{Safe UI methods:}  \CodeIn{View.post}
and \CodeIn{View.postDelay}, which execute code on the UI thread.

@@

\subsection{Android-specific Implementation Details}

>>>>

\item \textbf{Safe UI methods:}  \CodeIn{Display.asyncExec}
and \CodeIn{Display.syncExec}.
These methods
execute code (a)synchro\-nously in the UI thread.

@@

\tinystep
\tinystep
\subsubsection{Eclipse Plugin}

@@

\item \textbf{UI-accessing nodes} and \textbf{safe UI methods} are the same as SWT\@.

@@

\item \textbf{Safe UI methods:}  
\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{Swing\-Util\-ities.invokeAndWait}, which execute code in the UI thread.

@@

\item \textbf{Safe UI methods:}  \CodeIn{View.post}
and \CodeIn{View.postDelay}, which execute code in the UI thread.

@@

\subsection{Android-Specific Implementation Details}
